---
title: "Results"
author: "Yue"
date: "19 August 2016"
output:
  pdf_document: default
  html_document: default
---
# Results

```{r message = FALSE, warning = FALSE}
source('loadData.R')
usePackage('papaja')
apa_prepare_doc() # Prepare document for rendering

```

## Data quality analysis

The durations of key press from both production and reproduction were recorded during the task. For further analysis, we chose the trials that fit two criteria: 

1). Those trials with a key-press time from reproduction less or more than 50% of the tested intervals . By removing these trials, operations mistakes such as releasing keys accidentally or forgetting to release keys were excluded. 

2). Judging from the key press durations from production phase, those trials with a key release before the offset of the stimulus or after 1 second delay of the offset were excluded. These trials may suggest lapses of attention during the task.

After marking the trials as 'outliers' that fit those two criteria above, we also excluded data from the subjects that with a percentage of outliers above 30%, where 5 out of 49 participants were excluded from all sessions of the experiments. All the participants excluded were all from the sessions of visual modality (3 from the Mix session and 2 from the Block session). This result reflects higher noise level in visual modality, which partially confirmed our consideration at the first place that tasks of temporal reproduction in auditory domain may have higher precisions.


## Figure 1 mean reproduction and relative reproduction error

1. The mean reproductions monotonically increased with test intervals in all four sessions;
2. Under the Mix sessions,  participants tended to overestimate the short intervals and underestimate the long ones, this is the classic characteristic of 'central tendency' effect. To further illustrate this effect, we calculate the Relative Reproduction Error that was defined as the difference between the reproduction and the tested interval divided by the tested interval. This parameter represents how the estimation deviates from the actual interval, where the positive number indicates overestimation and negative number indicates underestimation. 
3. relative reproduction error.
(the whole range of the error) As is shown in figure2(right panel), we could see clearly how the response deviates from the actual duration. The maximum error in this study  was within 32%. This is a large improvement in accuracy compared to the previous study(Lewis et.) where the maximum deviation from the estimation on 68ms was approximately 500 percent. This result also partially confirmed our previous consideration that tasks of reproduction under 300ms may produce higher noise level. 

In general, the errors within sub-seconds range were relatively high where motor noise may still play an important role in the performance. The central tendency effect was clearly illustrated under the Mix condition from both modalities, where the short intervals (shortest three intervals) were overestimated and the long ones were overestimated. 

(Block condition)However, this same tendency of the deviations was not shown under block conditions.  Eight of nine intervals under block conditions were overestimated from both auditory and visual modality. Nevertheless, within the long block ranges from 9s to 16.8s, we could still see the central tendency effect, where the shortest intervals was estimated and the longest interval were overestimated. 

Seen from modality, responses from auditory modality showed less errors compare to the visual domain. 
## Central Tendency Effect

After removing the outliers through the criteria mentioned above, grand-averaged estimations against intervals from four sessions of this study were plotted in Figure 3(left penal). As shown in the results, estimations times monotonically increased with sample intervals.  A classic central tendency effect was shown from Mix sessions of both experiments, where subjects tended to overestimate the short intervals and overestimate the long intervals. 

By calculating the differences between mean estimations and the corresponding intervals, mean estimation errors are shown in the right penal of Figure 3. A clear central tendency effect was revealed especially during the long intervals of Mix sessions of both experiments, where negative values are shown indicating a underestimations of intervals.
In the meanwhile, smaller absolute values of reproduction errors indicate less bias from audition than vision, which is consistent with Cicchini’s study of interval timing (Cicchini 2012) that subjects responded veridically in auditory timing than visual timing.


```{r figure1, echo = FALSE, warning=FALSE, message=FALSE, fig.height= 6, fig.width=4}
 # mean estimation + mean relative reproduction error in one figure
 
 fig_mEstimation <- fig1 +aes(y = mRepr) +
   geom_abline(aes(intercept = 0, slope = 1),linetype = 2) +
   scale_x_continuous(trans = "log10")+
   scale_y_continuous(trans = "log10") +
   ylab("Mean Estimate(s)")
   
 fig_mRre <-  fig1 + aes(y = mRepErr/duration)  +
   geom_abline(aes(intercept = 0, slope = 0),linetype = 2) +   
   scale_x_continuous(trans = "log10") +  
   legend_pos(c(0.9,0.8))  + 
   ylim(-0.3,0.4) +
   ylab("Relative Reproduction Errors")
 
 
 library("Rmisc")
  multiplot(fig_mEstimation, fig_mRre, cols = 1)

```


## 

```{r figure_mean_cv, echo = FALSE, warning=FALSE, message=FALSE, fig.height= 3, fig.width=4}
 fig_mcv <- fig1 + aes(y=mCV) +
    geom_smooth(method = "lm", se = FALSE, linetype = 1, size = 0.4) +
    scale_x_continuous(trans = "log10") +
    ylab("Coefficient of Variance") + 
    ylim(0.1,0.45) +
    legend_pos(c(0.8,0.8))
 fig_mcv
 
```

##  Figure 4: sd of production/sd of reproduction

As has been mentioned above, motor noise from the task may play an important role in affecting the accuracy. 

The perceptual time is consist of the 'predicted' perceptual time and the noise(R = I + N). And the noise is consist of context biases and motor noise. 

(V_Rd)2 = (Vi)2 + (Vn)2

By calculating the ratio of variance between the production and reproduction, we could get the percentage of motor noise in the whole noise.

- Figure 5: Block-independent analysis

1. Mean values of the CVs 

We calculated the mean values of CVs from each block. By analyzing the data by blocks, we divided the tested intervals into three sub-groups: short, medium and long, where intervals from short group range within sub second(300ms to 900ms), medium group ranges from 1s to 9s and long group ranges from 11s to 16s.

## Inter-Trial Effects 

illustrates the central tendency effects more, in the Mix conditions(under three categories: longer, equal and shorter )
